### 2020-05-27 writeup/intro.tex
abstract submitted

\begin{abstract}
When does multi-task and transfer learning outperform single-task learning?
In this paper, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
\end{abstract}

>>>>

\begin{abstract}
When does multi-task and transfer learning outperform single-task learning?
In this work, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
\end{abstract}
